Computational tools for representation theory of affine Lie algebras

### 2009-07-26 AffineLieAlgebras/ACMS2009/article.tex
Bibliography work

Since the affine Lie algebras are infinite-dimensional extensions of simple finite-dimensional Lie algebras, their representation theory is well understood \cite{kac1990idl}, \cite{wakimoto2001idl}, \cite{Wakimoto-Second-Book}. But infinite dimensionality poses a challenge for computational methods.

@@

The first task is usually solved using the algorithms based on the recursive Freudenthal formula for weight multiplicities \eqref{eq:1}. The summation is optimized by considering of Weyl symmetry \cite{kass1990ala}, \cite{Moody-Patera}. While these algorithms are reasonably fast, the use of Racah-like recurrent relation \eqref{eq:2} is theoretically more efficient \cite{Nazarov2008}. In practice speed depends upon the realisation. So we describe this alternative approach in section \ref{sec:representations} and show results of practical speed comparisons.

>>>>

Since the affine Lie algebras are infinite-dimensional extensions of simple finite-dimensional Lie algebras, their representation theory is well understood \cite{kac1990idl}, \cite{wakimoto2001idl}, \cite{wakimoto2001lectures}. But infinite dimensionality poses a challenge for computational methods.

@@

The first task is usually solved using the algorithms based on the recursive Freudenthal formula for weight multiplicities \eqref{eq:1}. The summation is optimized by considering of Weyl symmetry \cite{kass1990ala}, \cite{moody1982fast}. While these algorithms are reasonably fast, the use of Racah-like recurrent relation \eqref{eq:2} is theoretically more efficient \cite{Nazarov2008}. In practice speed depends upon the realisation. So we describe this alternative approach in section \ref{sec:representations} and show results of practical speed comparisons.
